---
title: "Conditional Statements Exercises"
author: "HannahChang"
date: "2018年3月19日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For these exercises, use what you have learned about if,else if, and else statements to answer the questions! The first exercise is done for you as an example:

#####Example: Write a script that prints "Hello" if the variable x is equal to 1:

```{r Hello}
x <- 1

if (x ==1){
    print("Hello")
}
```


####Exercise Problems
####Ex 1: Write a script that will print "Even Number" if the variable x is an even number, otherwise print "Not Even":

```{r EX1}
x <- 4 # Change x to test

if (x%%2 == 0){
    print('Even Number')
}else{
    print('Not Even')
}
```


####Ex 2: Write a script that will print 'Is a Matrix' if the variable x is a matrix, otherwise print "Not a Matrix". Hint: You may want to check out help(is.matrix)

```{r EX2}
x <- matrix()

if (is.matrix(x)){
  print('Is a Matrix')
}else{
  print('Not a Matrix')
}
  
```


####Ex 3: Create a script that given a numeric vector x with a length 3, will print out the elements in order from high to low. You must use if,else if, and else statements for your logic. (This code will be relatively long)

```{r EX3}
x <- c(1,3,5)

if(x[1] > x[2]){
	temp = x[1]
	x[1] = x[2]
	x[2] = temp
}
if(x[1] > x[3]){
	temp = x[1]
	x[1] = x[3]
	x[3] = temp
}
if(x[2] > x[3]){
	temp = x[2]
	x[2] = x[3]
	x[3] = temp
}

print(paste(x[3], x[2], x[1]))
```


####Ex 4: Write a script that uses if,else if, and else statements to print the max element in a numeric vector with 3 elements.

```{r EX4}
x <- c(3,5,4)
if(x[1]>x[2] && x[1]>x[3]){
  print(x[1])
}else if(x[2]>x[3]){
  print(x[2])
}else{
  print(x[3])
}

```


####Great Job!